Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-09-27 prob.tex
prob.tex After meeting, delete the wrong(?) stories...

% \makeatletter
% \newtheoremstyle{indented}
%   {3pt}% space before
%   {3pt}% space after
%   {\addtolength{\@totalleftmargin}{3.5em}
%    \addtolength{\linewidth}{-3.5em}
%    \parshape 1 3.5em \linewidth}% body font
%   {}% indent
%   {\bfseries}% header font
%   {.}% punctuation
%   {.5em}% after theorem header
%   {}% header specification (empty for default)
% \makeatother
% \theoremstyle{indented}
\theoremstyle{remark}
\newtheorem{example}{Example}
\newtheorem{definition}{Definition}
\newtheorem{cor}{Corollary}
\newtheorem{lemma}{Lemma}
\newtheorem{thm}{Theorem}
\newtheorem{case}{Case}
\newcommand{\events}{\ensuremath{\mathcal{E}}}
\newcommand{\qevents}{\ensuremath{\mathcal{E}}}
\newcommand{\pmeas}{\ensuremath{\mu}}
\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\ps}{\texttt{+}}
\newcommand{\ms}{\texttt{-}}
\newcommand{\poss}{{\mbox{\wesa{possible}}}}
\newcommand{\imposs}{{\mbox{\wesa{impossible}}}}
\newcommand{\likely}{{\mbox{\wesa{likely}}}}
\newcommand{\unlikely}{{\mbox{\wesa{unlikely}}}}
\newcommand{\necess}{{\mbox{\wesa{certain}}}}
\newcommand{\overflow}{{\mbox{\wesa{overflow}}}}
\newcommand{\unknown}{{\mbox{\wesa{unknown}}}}

@@

The Bondareva-Shapley theorem can be used to algorithmically decide
non-empty core because the minimal balanced sets can be generated
by an algorithm~\cite{Peleg1965}. However, the number of minimal
balanced sets grows very rapidly with $\left|\Omega\right|$, the
size of $\Omega$~\cite{Shapley1967,Zhao2008}\footnote{\yutsung{Prove the number of minimal balanced sets grow exponentially
or more?}}, so that we have only verified every interval-valued probability
measure has a non-empty core when $\left|\Omega\right|\le5$ so far.\footnote{\yutsung{The program for $\left|\Omega\right|=6$ blows up the memory
again, and the symmetric answer doesn't really work. Hence, currently
only back-track randomized program still searches IVPM with a extremely
slow speed...}}

@@

@@

\yutsung{I think there are three possible approaches to complete
the story.

Our original plan was to put the Mermin v.s. Meyer debate here, and
move on to the discrete quantum probability measure. Then, discrete
real-valued quantum probability measures are expected to fail because
of John's proof, and we hope discrete interval-valued Gleason's theorem
can work in some sense? This story is scratched in section~\ref{sec:DQT}.
The problem is the discrete version of example~\ref{ex:three-dimensional-three-value}.
Because we don't really use $\mathbb{C}$ in example~\ref{ex:three-dimensional-three-value},
the discrete version of example~\ref{ex:three-dimensional-three-value}
is likely to serve as an counterexample for discrete interval-valued
Gleason's theorem... Hence, we may need to put some extra-conditions
to by-pass the discrete version of example~\ref{ex:three-dimensional-three-value}.

Another possible approach is to tell everybody: because Gleason's
theorem is an accident, the original way to formulate to a quantum
system as a state vector or density matrix is an accident. If we want
to do things correct, we should work on quantum (real/interval)-valued
probability measure directly. This approach is scratched in section~\ref{sec:QC}.
The problem of this approach is that we need an concrete example to
show it is possible to work on quantum (real/interval)-valued probability
measure directly. For example, we might need to verify tensor product
and quantum teleportation works in this model...

The other approach might be keep going section~\ref{sec:Quantum-Probability-Spaces},
but try to prove there is a unique interval-valued Born rule with
extra-conditions. I sketched a possible set of conditions, but haven't
verified whether it really works or not...}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{sec:DQT}(One possible approach) Discrete Quantum Theory}

\subsection{Discrete Quantum Real-valued Probability Measures}

Killed by John... Need to be typed...

\subsection{Discrete Quantum Interval-valued Probability Measures}

Discrete interval-valued Gleason's theorem should be here, but it
is unlikely to work if the discrete version of example~\ref{ex:three-dimensional-three-value}
works... Might need to put some extra-conditions to by-pass it...

Following are possible extra-conditions:
\begin{enumerate}
\item \emph{$\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $} is
too small...
\item $\mu\otimes\mu$ might not be a quantum real-valued probability measure,
where $\mu$ is a non-Born real-valued probability measure for dimension
2. Maybe embedding the small space into the bigger one could add extra-conditions
to kill strange interval-valued probability measures?
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\label{sec:QC}(Another possible approach) Quantum Computing on Quantum
(Real/Interval)-valued Probability Measures}

We give up the idea of representing a quantum state as a density matrix,
and compute the quantum state as a quantum (real/interval)-valued
probability measure directly.

\subsection{Time Evolution}

In CQT, an time evolution operator~$U$ will map a state~$\ket{\phi}$
to $U\ket{\phi}$. In this case, its quantum real-valued probability
measure after evolution is
\[
\mu_{U\ket{\phi}}^{B}\left(P\right)=\ip{\phi}{U^{\dagger}PU\phi}=\mu_{\ket{\phi}}^{B}\left(U^{\dagger}PU\right)\textrm{ .}
\]
Hence, given any quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$,
the quantum interval-valued probability measure after time evolution
operator~$U$ should be defined as 
\[
\bar{\mu}_{U}\left(P\right)=\bar{\mu}\left(U^{\dagger}PU\right)\textrm{ .}
\]

\subsection{Tensor Product and Partial Measurement}

\[
\left(\bar{\mu}_{1}\otimes\bar{\mu}_{2}\right)\left(P_{1}\otimes P_{2}\right)=\bar{\mu}_{1}\left(P_{1}\right)\bar{\mu}_{2}\left(P_{2}\right)?
\]
Is $\bar{\mu}_{1}\otimes\bar{\mu}_{2}$ still a quantum interval-valued
probability measure?

Might be hard, because $\mu\otimes\mu$ might not be a quantum real-valued
probability measure, where $\mu$ is a non-Born real-valued probability
measure for dimension 2.

Quantum Fubini Theorem?

\subsection{Quantum Teleportation}

\begin{figure}[t]
\[
\begin{array}{c}
\hspace{1cm}\xyC{.6em}\entrymodifiers={@*=<0em>}\xymatrix@R=0.9em{ & \ar@{.}[dddd] &  & \ar@{.}[dddd] &  & \ar@{.}[dddd] &  & \ar@{.}[dddd]\\
\lstick{\bar{\mu}} & \qw & \ctrl{1} & \qw & \gate{H} & \qw & \meter & \cw & \cw & \control\cw\\
 & \qw & \targ & \qw & \qw & \qw & \meter & \cw & \control\cw & \cwx & \ar@{.}[dd]\\
 & \qw & \qw & \qw & \qw & \qw & \qw & \qw & \gate{X}\cwx & \gate{Z}\cwx & \qw\\
 & \push{\bar{\mu}_{0}} &  & \push{\bar{\mu}_{1}} &  & \push{\bar{\mu}_{2}} &  & \push{\bar{\mu}_{3}} &  &  & \push{\bar{\mu}_{4}}
}
\end{array}
\]
\caption{\label{fig:QuantumTeleportation}Circuit for Quantum Teleportation}
\end{figure}

In figure~\ref{fig:QuantumTeleportation}, let $\ket{\phi}=\frac{1}{\sqrt{2}}\left(\ket{00}+\ket{11}\right)$.

$\bar{\mu}_{0}=\bar{\mu}_{1}\otimes\mu_{\ket{\phi}}^{B}$. Notice
that a quantum real-valued probability measure can be considered as
an special case of quantum interval-valued probability measure...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{(The other possible approach keep Section \ref{sec:Quantum-Probability-Spaces}) }

\subsection{Recover an Interval-valued Born Rule(?)}

Although not all interval-valued probability measure could correspond
to any real-valued probability measure as in theorem~\ref{def:EmptyCoreQuantumInterval-valuedProbability},
it does not mean we could not deduce an interval-valued Born rule.
Notice that Gleason's theorem only says every real-valued probability
measure can correspond to a mixed state by the Born rule, but does
not specify the Born rule should be the only rule which corresponds
a mixed state to a real-valued probability measure. For example, Gleason's
theorem does not rule out the correspondence $\mu_{\phi}^{\prime B}(P)=\melem{0}{P}{0}$
which send every state~$\ket{\phi}$ to the same real-valued probability
measure. If we want to recover the Born rule itself, we need to more
conditions to specify which state corresponds to which real-valued
probability measure.

\begin{thm}Consider\emph{ }$\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $.
There is a unique interval-valued Born rule~$\bar{\mu}^{B}:\left\{ \ket{\phi}\in\Hilb\middle|\ip{\phi}{\phi}=1\right\} \rightarrow\left(\events\rightarrow\mathscr{I}\right)$
such that:
\begin{itemize}
\item For any pure state~$\ket{\phi}$, $\bar{\mu}_{\phi}^{B}$ is an interval-valued
probability measure.
\item For any pure state~$\ket{\phi}$, $\bar{\mu}_{\phi}^{B}\left(\proj{\phi}\right)=\necess$.
\item For any pure state~$\ket{\phi}$, $\bar{\mu}_{\phi}^{B}\left(P\right)=\bar{\mu}_{\mathbf{U}\ket{\phi}}^{B}\left(\mathbf{U}P\mathbf{U}^{\dagger}\right)\textrm{ ,}$where
$\mathbf{U}$ is any unitary map, i.e., $\mathbf{U}^{\dagger}\mathbf{U}=\mathbb{1}$. 
\end{itemize}
\qed\end{thm}
\begin{proof}
? 
\end{proof}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{(The other possible approach keep Section \ref{sec:Quantum-Probability-Spaces}) }

\subsection{Question the original assumption(?)}

Although theorem~\ref{thm:Shapley} and \ref{def:EmptyCoreQuantumInterval-valuedProbability}
gives opposite results, their results are consistent. If we pick a
orthonormal basis~$\Omega=\left\{ \ket{\psi_{j}}\right\} _{j=1}^{d}$,
let $E\in2^{\Omega}$ be a classical event and $P=\tensor*[_{\mathscr{O}}]{\sum}{_{\ket{\psi_{j}}\in E}}\proj{\psi_{j}}$
be the quantum event corresponding to subspace span by $E$, we can
define a classical interval-valued probability measure$\bar{\mu}^{\Omega}\left(E\right)=\bar{\mu}\left(P\right)$.
There are two cases.

\begin{case}If $\ket{\psi_{1}}$ is either $\ket{0}$, $\ket{\ps}$,
or $\ket{\ps'}$, then we have

\[
\begin{array}{c@{\qquad\qquad}c}
\begin{array}{rcl}
\bar{\mu}^{\Omega}(\emptyset) & = & \imposs\\
\bar{\mu}^{\Omega}(\{\ket{\psi_{1}}\}) & = & \imposs\\
\bar{\mu}^{\Omega}(\{\ket{\psi_{2}}\}) & = & \unknown\\
\bar{\mu}^{\Omega}(\{\ket{\psi_{3}}\}) & = & \unknown
\end{array} & \begin{array}{rcl}
\bar{\mu}^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}}\}) & = & \unknown\\
\bar{\mu}^{\Omega}(\{\ket{\psi_{3}},\ket{\psi_{1}}\}) & = & \unknown\\
\bar{\mu}^{\Omega}(\{\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & \necess\\
\bar{\mu}^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & \necess
\end{array}\end{array}
\]
It is easy to verify that $\bar{\mu}^{\Omega}$ has an non-empty core,
and $\pmeas^{\Omega}:2^{\Omega}\rightarrow\left[0,1\right]$ is in
its core. 
\[
\begin{array}{c@{\qquad\qquad}c}
\begin{array}{rcl}
\pmeas^{\Omega}(\emptyset) & = & 0\\
\pmeas^{\Omega}(\{\ket{\psi_{1}}\}) & = & 0\\
\pmeas^{\Omega}(\{\ket{\psi_{2}}\}) & = & 1/2\\
\pmeas^{\Omega}(\{\ket{\psi_{3}}\}) & = & 1/2
\end{array} & \begin{array}{rcl}
\pmeas^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}}\}) & = & 1/2\\
\pmeas^{\Omega}(\{\ket{\psi_{3}},\ket{\psi_{1}}\}) & = & 1/2\\
\pmeas^{\Omega}(\{\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & 1\\
\pmeas^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & 1
\end{array}\end{array}
\]
\qed\end{case}

\begin{case}If neither $\ket{0}$, $\ket{\ps}$, nor $\ket{\ps'}$
is in $\Omega$, then we have

\[
\begin{array}{c@{\qquad\qquad}c}
\begin{array}{rcl}
\bar{\mu}^{\Omega}(\emptyset) & = & \imposs\\
\bar{\mu}^{\Omega}(\{\ket{\psi_{1}}\}) & = & \unknown\\
\bar{\mu}^{\Omega}(\{\ket{\psi_{2}}\}) & = & \unknown\\
\bar{\mu}^{\Omega}(\{\ket{\psi_{3}}\}) & = & \unknown
\end{array} & \begin{array}{rcl}
\bar{\mu}^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}}\}) & = & \unknown\\
\bar{\mu}^{\Omega}(\{\ket{\psi_{3}},\ket{\psi_{1}}\}) & = & \unknown\\
\bar{\mu}^{\Omega}(\{\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & \unknown\\
\bar{\mu}^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & \necess
\end{array}\end{array}
\]
In this case, $\pmeas^{\Omega}:2^{\Omega}\rightarrow\left[0,1\right]$
defined by the following is in the core of $\bar{\mu}^{\Omega}$.
\[
\begin{array}{c@{\qquad\qquad}c}
\begin{array}{rcl}
\pmeas^{\Omega}(\emptyset) & = & 0\\
\pmeas^{\Omega}(\{\ket{\psi_{1}}\}) & = & 1/3\\
\pmeas^{\Omega}(\{\ket{\psi_{2}}\}) & = & 1/3\\
\pmeas^{\Omega}(\{\ket{\psi_{3}}\}) & = & 1/3
\end{array} & \begin{array}{rcl}
\pmeas^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}}\}) & = & 1/3\\
\pmeas^{\Omega}(\{\ket{\psi_{3}},\ket{\psi_{1}}\}) & = & 1/3\\
\pmeas^{\Omega}(\{\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & 1/3\\
\pmeas^{\Omega}(\{\ket{\psi_{1}},\ket{\psi_{2}},\ket{\psi_{3}}\}) & = & 1
\end{array}\end{array}
\]
\qed\end{case}

\section{(The other possible approach keep Section \ref{sec:Quantum-Probability-Spaces}) }

\subsection{Examples for Quantum Interval-valued Probability Measures}

@@

\begin{example}[Three-dimensional quantum 4-value interval-valued
probability measure]\label{ex:three-dimensional-4-value} \footnote{\yutsung{Need to verify whether this example is convex or not.}}Given
a three dimensional Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
Consider\emph{ }$\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $,
$\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$, $\ket{\ms}=\frac{1}{\sqrt{2}}(\ket{0}-\ket{1})$,
and a quantum $\mathscr{I}$-interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
defined as follow, where the state vectors corresponding to 1-dimensional
projector are also illustrated in figure~\ref{fig:three-dimensional-4-value}.
\begin{enumerate}
\item Let 
\begin{eqnarray*}
\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps}) & = & \imposs\\
\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0})=\bar{\mu}(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\ps}) & = & \necess\textrm{ ,}
\end{eqnarray*}
 where $\ket{0}$ and $\ket{\ps}$ is illustrated as the red and green
dotted vector, respectively.
\item Consider the red and green circles in figure~\ref{fig:three-dimensional-4-value}.
They are the states orthogonal to $\ket{0}$ and $\ket{\ps}$, respectively,
and can be parametrized as $\ket{0_{\theta,\gamma}^{\perp}}=\rme^{\rmi\gamma}\sin\theta\ket{1}+\cos\theta\ket{2}$
and $\ket{\ps_{\theta,\gamma}^{\perp}}=-\rme^{\rmi\gamma}\sin\theta\ket{\ms}+\cos\theta\ket{2}$,
where $0\le\theta\le\frac{\pi}{2}$ and $0\le\gamma<2\pi$. The dotted
half of those states need special treatment, i.e., when where $0\le\theta<\frac{\pi}{2}$
and $0\le\gamma<\pi$, we define 
\begin{eqnarray*}
\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=\bar{\mu}\left(\proj{\ps_{\theta,\gamma}^{\perp}}\right) & = & \likely\\
\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\theta,\gamma}^{\perp}}\right)=\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\ps_{\theta,\gamma}^{\perp}}\right) & = & \unlikely\textrm{ .}
\end{eqnarray*}
\item Otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$ and $\bar{\mu}(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi})=\likely$. 
\end{enumerate}
That $\bar{\mu}$ has an empty core can be proved by contradiction.
Assume there is a real-valued probability measure satisfying $\mu_{\rho}^{B}(P)\in\bar{\mu}(P)$
for all $P\in\events$. Because $\mu_{\rho}^{B}(\proj{0})\in\bar{\mu}(\proj{0})=\imposs$
and $\mu_{\rho}^{B}(\proj{\ps})\in\bar{\mu}(\proj{\ps})=\imposs$,
we must have $\mu_{\rho}^{B}(\proj{0})=\mu_{\rho}^{B}(\proj{\ps})=0$
so that $\mu_{\rho}^{B}=\mu_{\ket{2}}^{B}$. However, 
\[
\mu_{\ket{2}}^{B}(\proj{2})=1\notin\unlikely=\bar{\mu}(\proj{2})\textrm{ .}
\]

>>>>

% \makeatletter
% \newtheoremstyle{indented}
%   {3pt}% space before
%   {3pt}% space after
%   {\addtolength{\@totalleftmargin}{3.5em}
%    \addtolength{\linewidth}{-3.5em}
%    \parshape 1 3.5em \linewidth}% body font
%   {}% indent
%   {\bfseries}% header font
%   {.}% punctuation
%   {.5em}% after theorem header
%   {}% header specification (empty for default)
% \makeatother
% \theoremstyle{indented}
\theoremstyle{remark}
\newtheorem{example}{Example}
\newtheorem{definition}{Definition}
\newtheorem{cor}{Corollary}
\newtheorem{lemma}{Lemma}
\newtheorem{thm}{Theorem}
\newtheorem{case}{Case}
\newtheorem{conjecture}{Conjecture}
\newcommand{\events}{\ensuremath{\mathcal{E}}}
\newcommand{\qevents}{\ensuremath{\mathcal{E}}}
\newcommand{\pmeas}{\ensuremath{\mu}}
\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\ps}{\texttt{+}}
\newcommand{\ms}{\texttt{-}}
\newcommand{\poss}{{\mbox{\wesa{possible}}}}
\newcommand{\imposs}{{\mbox{\wesa{impossible}}}}
\newcommand{\likely}{{\mbox{\wesa{likely}}}}
\newcommand{\unlikely}{{\mbox{\wesa{unlikely}}}}
\newcommand{\necess}{{\mbox{\wesa{certain}}}}
\newcommand{\overflow}{{\mbox{\wesa{overflow}}}}
\newcommand{\unknown}{{\mbox{\wesa{unknown}}}}

@@

The Bondareva-Shapley theorem can be used to algorithmically decide
non-empty core because the minimal balanced sets can be generated
by an algorithm~\cite{Peleg1965}. However, the number of minimal
balanced sets grows very rapidly with $\left|\Omega\right|$, the
size of $\Omega$~\cite{Shapley1967,Zhao2008}\footnote{\yutsung{Prove the number of minimal balanced sets grow exponentially
or more?}}, so that we have only verified every interval-valued probability
measure has a non-empty core when $\left|\Omega\right|\le5$ so far.\footnote{\yutsung{The program for $\left|\Omega\right|=6$ blows up the memory
again, and the symmetric answer doesn't really work. Hence, currently
only back-track randomized program still searches IVPM with a extremely
slow speed...}} Based on the previous fact, we have the following conjecture.

\begin{conjecture}Every interval-valued probability measure has a
nonempty core.\qed\end{conjecture}

@@

Recall that when approximating the probability classically, the quality
of the experimental equipment cannot be compensated by the number
of independent trials. If the precision of the intervals~$\mathscr{I}$
represents the quality of the quantum experimental equipment, example~\ref{ex:three-dimensional-three-value}
tells us that we cannot identify a particular state if the experimental
equipment reveals too little information.

@@

\appendix
%%%%%

\section{Examples for Quantum Interval-valued Probability Measures}

@@

\begin{example}{[}Three-dimensional quantum 4-value interval-valued
probability measure{]}\label{ex:three-dimensional-4-value} \footnote{\yutsung{Need to verify whether this example is convex or not.}}Given
a three dimensional Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
Consider\emph{ }$\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $,
$\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$, $\ket{\ms}=\frac{1}{\sqrt{2}}(\ket{0}-\ket{1})$,
and a quantum $\mathscr{I}$-interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
defined as follow, where the state vectors corresponding to 1-dimensional
projector are also illustrated in figure~\ref{fig:three-dimensional-4-value}.
\begin{enumerate}
\item Let 
\begin{eqnarray*}
\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps}) & = & \imposs\\
\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0})=\bar{\mu}(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\ps}) & = & \necess\textrm{ ,}
\end{eqnarray*}
 where $\ket{0}$ and $\ket{\ps}$ is illustrated as the red and green
dotted vector, respectively.
\item Consider the red and green circles in figure~\ref{fig:three-dimensional-4-value}.
They are the states orthogonal to $\ket{0}$ and $\ket{\ps}$, respectively,
and can be parametrized as $\ket{0_{\theta,\gamma}^{\perp}}=\rme^{\rmi\gamma}\sin\theta\ket{1}+\cos\theta\ket{2}$
and $\ket{\ps_{\theta,\gamma}^{\perp}}=-\rme^{\rmi\gamma}\sin\theta\ket{\ms}+\cos\theta\ket{2}$,
where $0\le\theta\le\frac{\pi}{2}$ and $0\le\gamma<2\pi$. The dotted
half of those states need special treatment, i.e., when where $0\le\theta<\frac{\pi}{2}$
and $0\le\gamma<\pi$, we define 
\begin{eqnarray*}
\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=\bar{\mu}\left(\proj{\ps_{\theta,\gamma}^{\perp}}\right) & = & \likely\\
\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\theta,\gamma}^{\perp}}\right)=\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\ps_{\theta,\gamma}^{\perp}}\right) & = & \unlikely\textrm{ .}
\end{eqnarray*}
\item Otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$ and $\bar{\mu}(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi})=\likely$. 
\end{enumerate}
That $\bar{\mu}$ has an empty core can be proved by contradiction.
Assume there is a real-valued probability measure satisfying $\mu_{\rho}^{B}(P)\in\bar{\mu}(P)$
for all $P\in\events$. Because $\mu_{\rho}^{B}(\proj{0})\in\bar{\mu}(\proj{0})=\imposs$
and $\mu_{\rho}^{B}(\proj{\ps})\in\bar{\mu}(\proj{\ps})=\imposs$,
we must have $\mu_{\rho}^{B}(\proj{0})=\mu_{\rho}^{B}(\proj{\ps})=0$
so that $\mu_{\rho}^{B}=\mu_{\ket{2}}^{B}$. However, 
\[
\mu_{\ket{2}}^{B}(\proj{2})=1\notin\unlikely=\bar{\mu}(\proj{2})\textrm{ .}
\]
